### 2019-03-09 paper/sex_selection_spacing-ver2.tex
Prettier main results graphs with proper information

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
\caption{low education}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
\caption{med education}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
\caption{high education}
\end{figure}

>>>>

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
% \\
% \caption*{Rural}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
% \caption{low education}
% \label{fig:bootstrap_low}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with no education}
\label{fig:bootstrap_low}
\end{figure}

@@

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
% \\
% \caption*{Rural}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
% \caption{med education}
% \label{fig:bootstrap_med}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with one to seven years of education}
\label{fig:bootstrap_med}
\end{figure}

@@

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
% \\
% \caption*{Rural}
% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
% \caption{high education}
% \label{fig:bootstrap_high}
% \end{figure}

% \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education}
\label{fig:bootstrap_high}
\end{figure}
